%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 8 February 2019
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,]{moderncv}

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{3873B3}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[scaled=0.86]{DejaVuSansMono}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\def\donothing#1{#1}
\def\emaillink#1{#1}

%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75,footskip=60pt]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...



% personal data
\name{Benjamin}{Marmont}
\title{Student (Master of Management, Economics)}

\phone[mobile]{+64 21 0269 2180} % Phone number
\email{\donothing{\href{mailto:BLMarmont@xtra.co.nz}{\nolinkurl{BLMarmont@xtra.co.nz}}}}
 % Personal website
\social[linkedin]{www.linkedin.com/in/ben-marmont}

\social[github]{\url{https://github.com/BenMarmont}}
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted




% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle



\hypertarget{experience}{%
\section{Experience}\label{experience}}

\begin{itemize}
\tightlist
\item
  INDUSTRY MASTER OF MANAGEMENT (ECONOMICS)• DAIRYNZ• 2021 -- 2022 While
  completing my postgraduate degree with the support of DairyNZ, I
  situate myself in their Newstead office during the week. This allows
  me to leverage available resources and relationships, such as
  conference attendance (Pasture Summit, NZIPIM, NZAE, NZARES), farm
  walks, presentations, expert consultations, and peer feedback.
\item
  TEACHING AND RESEARCH ASSISTANT • UNIVERSITY OF WAIKATO • 2022 -- 2022
  I assisted in the first 'R for Data Science course of its type at this
  university for a semester. For most of the course, I was the sole
  assistant for a class of more than thirty students. After completing
  this course, I began working as a Research Assistant on converting an
  existing excel CBA into a general model in R.
\item
  ECONOMIC ANALYST • URBAN ECONOMICS • 2021 -- 2021 After completing my
  undergraduate degree, I worked a term contract at this consultancy,
  where I developed my analytical skills in a property economics
  application.
\end{itemize}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\begin{itemize}
\tightlist
\item
  Problem Solving
\item
  Presentation
\item
  Communication
\item
  Analysis
\item
  Teaching
\item
  R
\item
  Teamwork
\end{itemize}

\hypertarget{education}{%
\section{Education}\label{education}}

\nopagebreak
    \cventry{1889-91}{Informal studies}{Flying University}{Warsaw, Poland}{}{\empty}
    \cventry{1893}{Master of Physics}{Sorbonne Université}{Paris, France}{}{\empty}
    \cventry{1894}{Master of Mathematics}{Sorbonne Université}{Paris, France}{}{\empty}

\hypertarget{education-1}{%
\section{Education}\label{education-1}}

\nopagebreak
    \cvitem{2022}{Degree Master of Management (Economics). My research investigates a novel approach to methane mitigation in NZ’s dairy industry utilising in-paddock smart-feeders as a delivery mechanism for methane inhibitors. It contains two distinct pieces, the adoption diffusion of the approach throughout NZ’s dairy farming population and the approach’s economic performance in different scenarios. Each piece has modelling to quantify the issues at hand.}
    \cvitem{2020}{Degree Bachelor of Business (Economics). While studying at Massey, I majored in economics and minored in finance. During this time, I undertook an exchange to Purdue University in the United States to study agricultural economics, driven by a desire to study behavioural economics, which was not offered domestically at the time.}

\hypertarget{volunteer-experience}{%
\section{Volunteer Experience}\label{volunteer-experience}}

Health and Safety Officer -- University of Waikato Rugby Club. Treasurer
of Massey University Student Enterprise. Secretary of Massey University
Ultimate Frisbee Club. Secretary of Massey University Auckland
Underwater Club.

\hypertarget{achievements}{%
\section{Achievements}\label{achievements}}

Recipient of the NZARES post-graduate award. Recipient of the Flower
Agribusiness conference participation award (used to attend NZAE.)
Recipient of the DairyNZ research masters scholarship. Recipient of the
Fuji Xerox Global exchange scholarship. Recipient of the UHY Haines
Norton business student scholarship.


\end{document}

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
