---
name: Benjamin    
surname: Marmont
position: "Economist"
phone: +64 21 0269 2180
email: "BLMarmont@xtra.co.nz"
github: BenMarmont
linkedin: Ben-Marmont
www: researchgate.net/profile/Ben-Marmont
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# Objective

Since completing my Masters of Management (Economics) at the University of Waikato I have worked at DairyNZ as an Economist, deepening my understanding of Agricultural Economics, the Dairy sector and connected primary industries. Moving forward my aim is to continue applying the knowledge and skills I have developed, and add to them.

# Experience

```{r}
tribble(
  ~when, ~what,~with, ~why,
  "2023-Present", "Economist", "DairyNZ", "After completing my Masters at DairyNZ I transitioned into a role in their Economics team, where I was part of several pieces of work often relating to surfacing data and related analyses via industry publications or the teams public facing dashboard. In addition I also undertook analysis to support a business case, delivered two R (R is a statistical programming language) courses, attended conferences, and published two papers relating to the research I undertook during my masters in this time",
  "2021-2022", "Industry Master of Management (Economics)", "DairyNZ", "While completing my postgraduate degree with the support of DairyNZ, I situate myself in their Newstead office during the week. This allows me to leverage those resources and relationships available to me, such as conference attendance (Pasture Summit, NZIPIM, NZAE, NZARES), farm walks, presentations, expert consultations, and peer feedback. By accepting such opportunities I have developed significant knowledge of the dairy industry and wider agricultural sector",
  # "2022", "Teaching and Research Assistant", "University of Waikato","I was a TA on the first ‘R for Data Science' course of its type at this university for a semester. I was the primary TA for a class of more than thirty students. After the completion of this course I began working as a Research Assistant working on converting an existing Excel case study CBA into a model adaptable for serveral case studies. This work was undetaken in R",
  "2021", "Economic Analyst", "Urban Economics","After completing my undergraduate degree I worked a term contract at this consultancy, where I developed my analytical skills in a property economics application including extensive work on a gravity model of the retirement villages in Auckland"
) %>% 
  detailed_entries(
   what, with,when,    
   why)
    
    

    # glue::glue("Degree in {Type}"),
    
```

\newpage

# Education

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  "2021-2022", "Master of Management (Economics) - First Class Honours", "My research at the University of Waikato investigated a novel approach to the methane mitigation in NZ’s dairy industry utilising in-paddock smart-feeders as a delivery mechanism for methane inhibitors. It contains two distinct pieces, the adoption diffusion of the approach throughout NZ’s dairy farming population and the approach’s economic performance in different scenarios. Each piece has modelling to quantify the issues at hand.",
  "2018-2020", "Bachelor of Business (Economics)", "While studying at Massey, I majored in economics and minored in finance. During this time, I undertook an exchange to Purdue University in the United States to study agricultural economics, driven by a desire to study behavioural economics, which was not offered domestically at the time."
) %>% 
  brief_entries(
    glue::glue("{Type}"),
    Year, 
    Desc
  )
```

# Skills

-   Problem Solving

-   Presentation

-   Communication

-   Analysis

-   Teaching

-   R

-   <div>

    # Volunteer Experience

    </div>

-   Health and Safety Officer -- University of Waikato Rugby Club.

-   Treasurer of Massey University Student Enterprise.

-   Secretary of Massey University Ultimate Frisbee Club.

-   Secretary of Massey University Auckland Underwater Club.

# Achievements

-   NZARES post-graduate award.
-   Flower Agribusiness conference participation award.
-   DairyNZ research masters scholarship.
-   Fuji Xerox Global exchange scholarship.
-   UHY Haines Norton business student scholarship.

# Hobbies

Outside of work I love to get outdoors, be it playing a Rugby, Ultimate Frisbee, Freediving, Mountain Biking or Fishing. My enjoyment of the outdoors was a major driver towards my move to the Waikato where I could have an impact environmental outcomes.
