---
name: Benjamin    
surname: Marmont
position: "Student (Master of Management, Economics)"
phone: +64 21 0269 2180
email: "BLMarmont@xtra.co.nz"
github: BenMarmont
linkedin: Ben-Marmont
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

# Experience

 * INDUSTRY MASTER OF MANAGEMENT (ECONOMICS)• DAIRYNZ• 2021 – 2022
While completing my postgraduate degree with the support of DairyNZ, I situate myself in their Newstead office during the week. This allows me to leverage available resources and relationships, such as conference attendance (Pasture Summit, NZIPIM, NZAE, NZARES), farm walks, presentations, expert consultations, and peer feedback. 
 * TEACHING AND RESEARCH ASSISTANT • UNIVERSITY OF WAIKATO • 2022 – 2022
I assisted in the first ‘R for Data Science course of its type at this university for a semester. For most of the course, I was the sole assistant for a class of more than thirty students. After completing this course, I began working as a Research Assistant on converting an existing excel CBA into a general model in R.
 * ECONOMIC ANALYST • URBAN ECONOMICS • 2021 – 2021
After completing my undergraduate degree, I worked a term contract at this consultancy, where I developed my analytical skills in a property economics application.

# Skills

 * Problem Solving
 * Presentation
 * Communication
 * Analysis
 * Teaching
 * R
 * Teamwork
 
# Education

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2022, "Master of Management (Economics)", "My research investigates a novel approach to methane mitigation in NZ’s dairy industry utilising in-paddock smart-feeders as a delivery mechanism for methane inhibitors. It contains two distinct pieces, the adoption diffusion of the approach throughout NZ’s dairy farming population and the approach’s economic performance in different scenarios. Each piece has modelling to quantify the issues at hand.",
  2020, "Bachelor of Business (Economics)", "While studying at Massey, I majored in economics and minored in finance. During this time, I undertook an exchange to Purdue University in the United States to study agricultural economics, driven by a desire to study behavioural economics, which was not offered domestically at the time."
) %>% 
  brief_entries(
    glue::glue("Degree {Type}"),
    Year, 
    Desc
  )
```

# Volunteer Experience

Health and Safety Officer – University of Waikato Rugby Club.
Treasurer of Massey University Student Enterprise.
Secretary of Massey University Ultimate Frisbee Club.
Secretary of Massey University Auckland Underwater Club.

# Achievements
Recipient of the NZARES post-graduate award.
Recipient of the Flower Agribusiness conference participation award (used to attend NZAE.)
Recipient of the DairyNZ research masters scholarship.
Recipient of the Fuji Xerox Global exchange scholarship.
Recipient of the UHY Haines Norton business student scholarship.

